Liveness-Based Garbage Collection

### 2014-11-10 paper/sections/liveness.tex
liveness version 0

%==============================================================
\begin{figure}[t]  
% \footnotesize
\begin{eqnarray*}
\mathit{ref\/}(\kappa,\sigma,\Lfonly)
          &=& \{\,\} \mbox{, for $\kappa$ a constant, including $\NIL$}\\
\mathit{ref\/}((\CONS~x~y),\sigma,\Lfonly)
          &=& \{x.\alpha \mid \acar\alpha \in \sigma\} \cup \{y.\alpha \mid \acdr\alpha \in \sigma\} \\
\mathit{ref\/}((\CAR~x),\sigma,\Lfonly)
          &=&    \begin{array}{l l}
                    \{x.\epsilon\} \cup \{x.\acar\alpha \mid \alpha \in
\sigma\}, & \mbox{if}~\sigma \ne \emptyset\\
                    \emptyset  & \mbox{otherwise}
                 \end{array} \\
\mathit{ref\/}((\CDR~x),\sigma,\Lfonly)
          &=&    \begin{array}{l l}
                    \{x.\epsilon\} \cup \{x.\acdr\alpha \mid \alpha \in
\sigma\}, & \mbox{if}~\sigma \ne \emptyset\\
                    \emptyset  & \mbox{otherwise}
                 \end{array} \\
\mathit{ref\/}((\PRIM~x~y),\sigma,\Lfonly)
          &=&    \begin{array}{l l}
                    \{x.\epsilon, y.\epsilon\},  & \mbox{if}~\sigma \ne \emptyset\\
                    \emptyset  & \mbox{otherwise}
                 \end{array} \\
\mathit{ref\/}((\NULLQ~x),\sigma,\Lfonly)
          &=&    \begin{array}{l l}
                    \{x.\epsilon\},  & \mbox{if}~\sigma \ne \emptyset\\
                    \emptyset  & \mbox{otherwise}
                 \end{array} \\
\mathit{ref\/}((f~\myvec{x}),\sigma,\Lfonly)
%          &=& \bigcup_{i=1}^n y_i.\Lf{f}{i}{\sigma}
          &=&  \begin{array}{@{}l}  % to discourage \displaystyle
               \bigcup_{i=1}^n x_i.\Lf{f}{i}{\sigma}
               \end{array}
%          &=& \bigcup \{y_i.\Lf{f}{i}{\sigma} \mid i=1,\ldots, n\}
\\[1ex]
\mathcal{L}((\RETURN~x),\sigma,\Lfonly) &=& x.\sigma \\
\mathcal{L}((\SIF~x~e_1~e_2),\sigma,\Lfonly) &=&
        \begin{array}{l l}
                    \mathcal{L}(e_1,\sigma,\Lfonly) \cup
        \mathcal{L}(e_2,\sigma,\Lfonly) \cup
        \{x.\epsilon\},  & \mbox{if}~\sigma \ne \emptyset\\
                    \mathcal{L}(e_1,\sigma,\Lfonly) \cup
        \mathcal{L}(e_2,\sigma,\Lfonly)  & \mbox{otherwise}
                 \end{array} \\
        \mathcal{L}(\LET~\myvec{x} \leftarrow \myvec{s}~\IN~e),\sigma,\Lfonly) &=&
        \Lv
           \setminus \{\myvec{x}.*\}
           \cup LE(L)
\mbox{ where } \Lv = \lfloor\mathcal{L}(e,\sigma,\Lfonly)\rfloor_{\myvec{x}}
\end{eqnarray*}

\begin{minipage}{0.85\textwidth}
\infrule[live-define]
        {\mathcal{L}(e_f,\sigma,\Lfonly) = 
           \bigcup_{i=1}^n z_i.\Lf{f}{i}{\sigma}
              \mbox{ for each $f$ and $\sigma$}
        }
        { d_1 \ldots d_k \len \Lfonly
\\ \makebox[0mm]{where
     $(\DEFINE\ (f\ z_1\ \ldots\ z_n)\ \ e_f)$ is a member of $d_1 \ldots d_k$}}
\end{minipage}
\begin{minipage}{0.85\textwidth}
 \infrule[live-let-define]
         {f~\stackrel{\text{\tiny def}}{=}~(\DEFINE~(f~ x)~(\SIF~*~x~s[(f~ x)/x],~\mbox{and}~\Ldonly_{x \leftarrow s}~\stackrel{\text{\tiny def}}{=}~\Lfonly_f}       
         { x \leftarrow s \len \Ldonly_{x \leftarrow s}}
\end{minipage}
\normalsize
  \caption{Liveness equations and judgement rule}\label{fig:live-judge}
\end{figure}

>>>>

%==============================================================
\begin{figure}[t]  
% \footnotesize
\begin{eqnarray*}
\mathit{ref\/}(\kappa,\sigma,\Lfonly)
          &=& \{\,\} \mbox{, for $\kappa$ a constant, including $\NIL$}\\
\mathit{ref\/}((\CONS~x~y),\sigma,\Lfonly)
          &=& \{x.\alpha \mid \acar\alpha \in \sigma\} \cup \{y.\alpha \mid \acdr\alpha \in \sigma\} \\
\mathit{ref\/}((\CAR~x),\sigma,\Lfonly)
          &=&    \begin{array}{l l}
                    \{x.\epsilon\} \cup \{x.\acar\alpha \mid \alpha \in
\sigma\}, & \mbox{if}~\sigma \ne \emptyset\\
                    \emptyset  & \mbox{otherwise}
                 \end{array} \\
\mathit{ref\/}((\CDR~x),\sigma,\Lfonly)
          &=&    \begin{array}{l l}
                    \{x.\epsilon\} \cup \{x.\acdr\alpha \mid \alpha \in
\sigma\}, & \mbox{if}~\sigma \ne \emptyset\\
                    \emptyset  & \mbox{otherwise}
                 \end{array} \\
\mathit{ref\/}((\PRIM~x~y),\sigma,\Lfonly)
          &=&    \begin{array}{l l}
                    \{x.\epsilon, y.\epsilon\},  & \mbox{if}~\sigma \ne \emptyset\\
                    \emptyset  & \mbox{otherwise}
                 \end{array} \\
\mathit{ref\/}((\NULLQ~x),\sigma,\Lfonly)
          &=&    \begin{array}{l l}
                    \{x.\epsilon\},  & \mbox{if}~\sigma \ne \emptyset\\
                    \emptyset  & \mbox{otherwise}
                 \end{array} \\
\mathit{ref\/}((f~\myvec{x}),\sigma,\Lfonly)
%          &=& \bigcup_{i=1}^n y_i.\Lf{f}{i}{\sigma}
          &=&  \begin{array}{@{}l}  % to discourage \displaystyle
               \bigcup_{i=1}^n x_i.\Lf{f}{i}{\sigma}
               \end{array}
%          &=& \bigcup \{y_i.\Lf{f}{i}{\sigma} \mid i=1,\ldots, n\}
\\[1ex]
\mathcal{L}((\RETURN~x),\sigma,\Lfonly) &=& \{l \mapsto x.\sigma\}, \makebox[0mm]{\hspace*{3cm} where $l$ is a new label} \\
\mathcal{L}((\SIF~x~e_1~e_2),\sigma,\Lfonly) &=&
        \begin{array}{l l}
                    \mathcal{L}(e_1,\sigma,\Lfonly) \uplus
        \mathcal{L}(e_2,\sigma,\Lfonly) \uplus
        \{l \mapsto  \{x.\epsilon\}\},  & \mbox{if}~\sigma \ne \emptyset\\
        \emptyset  & \mbox{otherwise}
                 \end{array} \\
 \makebox[0mm]{\hspace*{3.8cm} where $l$ is a new label}\\
\mathcal{L}(\LET~x \leftarrow~s~\IN~e),\sigma,\Lfonly) &=&
        \{ l \mapsto \Ldonly_{x \leftarrow s}(\Lv(x)) \mid l \mapsto \Lv
        \in \mathcal{M}\}
\mbox{ where } \mathcal{M} = \mathcal{L}(e,\sigma,\Lfonly)\\
\Ldonly_{x \leftarrow s} &=& \Lfonly_f, \mbox{where}~f~\mbox{is a new function}\\
 \makebox[0mm]{\hspace*{7cm}   
 $(\DEFINE~(f\,x_1\,x_2\, \ldots \, x_n)~(\SIF\,*~x~s[(f\,x_1\,
           x_2\, \ldots\, x_n)/x]))$,} \\
 \makebox[0mm]{\hspace*{5.5cm} and 
     $(\ x_1\, \ldots\, x_n)$ are the variables in $s$}
\end{eqnarray*}

\begin{minipage}{0.85\textwidth}
\infrule[live-define]
        {\mathcal{L}(e_f,\sigma,\Lfonly) = 
           \bigcup_{i=1}^n z_i.\Lf{f}{i}{\sigma}
              \mbox{ for each $f$ and $\sigma$}
        }
        { d_1 \ldots d_k \len \Lfonly
\\ \makebox[0mm]{where
     $(\DEFINE\ (f\ z_1\ \ldots\ z_n)\ \ e_f)$ is a member of $d_1 \ldots d_k$}}
\end{minipage}

\bigskip
\begin{center}
\begin{minipage}{0.85\textwidth}
\end{minipage}
\end{center}
%% \begin{minipage}{0.85\textwidth}
%%  \infrule[live-let-define]
%%          {f~\stackrel{\text{\tiny def}}{=}~(\DEFINE~(f~x_1
%%            ~x_2 \ldots x_n)~(\SIF~*~x~s[(f~x_1~
%%            x_2\ldots x_n)/x]),~\mbox{and}~\Ldonly_{x \leftarrow s}~\stackrel{\text{\tiny def}}{=}~\Lfonly_f}       
%%          { x \leftarrow s \len \Ldonly_{x \leftarrow s}
%% \\ \makebox[0mm]{where
%%      $(\ x_1\ \ldots\ x_n)$ are the variables in $s$}}
%% \end{minipage}
\normalsize
  \caption{Liveness equations and judgement rule}\label{fig:live-judge}
\end{figure}
